Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-01 paper.tex
Add heating rates graph
Add cumulative heat to table and fill in missing values

\begin{figure}
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
  \mycaption{Kinetic energy as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
  plot is a enlarged version of the first.}
\label{fig:kink_str8_ke-4}%
\end{figure}

@@

% \begin{figure}
%   \centering
%     \begin{subfigure}{0.49\textwidth}
%       \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
%       \caption{Kinetic Energy}
%       \label{fig:kink_ke-4}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}{0.49\textwidth}
%       \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
%       \caption{Growth rate estimation}
%       \label{fig:kink_ke_log-4}
%     \end{subfigure}
%   \mycaption{Kinetic energy as a function of time showing the development and
%   measured growth rates $\gamma$ and $\lambda$ of the flute and kink
%   instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
%   plot is a enlarged version of the first.}
% \label{fig:kink_str8_ke-4}%
% \end{figure}

@@

\begin{figure}
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
\mycaption{Kinetic energy as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased.}
\label{fig:kink_str8_ke-3}%
\end{figure}

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{Anisotropic}}& \multicolumn{2}{c}{\rev{Isotropic}} \\
&
$\eta=10^{-4}$ &
$\eta=10^{-3}$ &
\rev{$\eta=10^{-4}$} &
\rev{$\eta=10^{-3}$} \\
\midrule
Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79
& \rev{??} & \rev{??} \\
Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  &
\rev{--} & \rev{1.06}\\
Observed growth rate of kink $\lambda$ & 2.55 & 0.15 & \rev{2.97} & \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 &
\rev{--} & \rev{??}\\
Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 & \rev{--} & \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 & \rev{--} & \rev{??} \\
Observed axial wave number $k_{\text{kink}}$ & \rev{??} & \rev{??} & 4.57 & 4.53\\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Internal energy, with viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
  plot is a enlarged version of the first.}
\label{fig:kink_str8_ke-4}%
\end{figure*}

@@

@@

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased.}
\label{fig:kink_str8_ke-3}%
\end{figure*}

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
\rev{Theoretical average resistive linear growth rate of flute $\gamma_r$}
& 0.35 
& 0.33
& 1.26 
& 1.25 \\
Observed nonlinear growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\rev{Theoretical radius $\tilde{r}_s$ of peak resistive flute growth rate}
& 0.125 
& 0.125 
& 0.148 
& 0.140\\
Observed radius $r_s$ of peak flute growth rate
& 0.125 
& \rev{--} 
& 0.163 
& \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$
& 23.61 
& \rev{--} 
& 16.05 
& \rev{??} \\
Observed axial wave number $k_{\text{kink}}$
& \rev{??} 
& 4.57 
& \rev{??} 
& 4.53\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}
